prep_annotating

### 2022-06-14 code/prep_annotate.Rmd
play analysis from 1 group

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

@@

#for plotting

#Data import constants
date_start=lubridate::ymd('2021-07-19')
fig_path=here("figs")
read_data_path <- "data/processed_data/joined_data/"
```
# Summary Processing
## Read data

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))

@@

#for plotting
theme_set(theme_bw())
#Data import constants
date_start=lubridate::ymd('2021-07-19')
fig_path=here("figs")
read_data_path <- "data/processed_data/joined_data/"
```
# Summary Processing
## Read data

@@

# Sample analysis

To test that we're annotating usefully, try to do initial analysis on sample annotation.

Next steps:
- add in post-test reference expressions
- sbert and look at convergence / divergence
- inter-group differences/ correlations

```{r}
sample <- read_tsv("post_annotate_sample.tsv")

words <- sample %>% filter(!is.na(span)) %>% 
  mutate(numchar=str_length(span),
         numword=str_count(span, "\\W+") + 1)
```

How many words of referring language are there per round?

sum_words <- words %>% group_by(trialNum) %>% summarize(sum_char=sum(numchar),
                                           sum_word=sum(numword))

  ggplot(sum_words,aes(x=trialNum,y=sum_char))+geom_point()+geom_smooth()
  ggplot(sum_words,aes(x=trialNum,y=sum_word))+geom_point()+geom_smooth()

How long are individual referring expressions?

  ggplot(words,aes(x=trialNum,y=numchar))+geom_point()+geom_smooth()
  ggplot(words,aes(x=trialNum,y=numword))+geom_point()+geom_smooth()

How many referring expressions are there?
```{r}
  ggplot(words,aes(x=trialNum))+geom_bar()

ggplot(words,aes(x=as.factor(referent)))+geom_bar()
```

  ggplot(words,aes(x=trialNum,y=numchar, color=as.factor(referent)))+geom_point()+geom_smooth(method="lm",se=F)
  ggplot(words,aes(x=trialNum,y=numword, color=as.factor(referent)))+geom_point()+geom_smooth(method="lm", se=F)
